### 2025-09-25 paper/sec/authoring-workflow.tex
Tweaks.

\item \textbf{Code synthesis step.} The expression synthesis step is an error-guided iterative prompting
loop~\citep{skreta23}, beginning with an initial prompt sent to the LLM (\secref{prompt-design} below)
requesting the generation of an expression $e$. Using the Fluid command-line interface, the expression is
validated to check that it evaluates without error, produces a value coercible to a string $s'$, and finally
that $s'$ is equal to the target fragment $s$. Any failure triggers prompt augmentation with the appropriate
error message and the system retries generation. If code synthesis loop is able to yield an expression which
computes $s$ within a maximum number of retries, the synthesis step succeeds with $e$. If the last generated
$e$ was invalid (resulting in an error), the code synthesis step fails with no expression. Otherwise, code
synthesis produces an expression $e$ but with a mismatched string outcome $s' \neq s$.

@@

The \InterpretationAgent is guided by a structured system prompt that frames code generation as a precise
replacement task. The model receives the imported datasets, helper modules, and the current Fluid
representation of the paragraph, in which a text fragment is marked with the tag \kw{[REPLACE …]}. Its task is
to substitute this placeholder with a Fluid expression that evaluates exactly to the target string,
reconstructing quantitative or comparative claims as data queries. To ensure integration with the workflow,
the output must consist solely of a syntactically valid Fluid expression, with no additional commentary. The
full prompt is given in~\appref{system-prompt:interpretation-agent}.

>>>>

\item \textbf{Code synthesis step.} The expression synthesis step is an error-guided iterative prompting
loop~\citep{skreta23}, beginning with an initial prompt sent to the LLM (see \emph{Prompt design} below)
requesting the generation of an expression $e$. Using the Fluid command-line interface, the expression is
validated to check that it evaluates without error, produces a value coercible to a string $s'$, and finally
that $s'$ is equal to the target fragment $s$. Any failure triggers prompt augmentation with the appropriate
error message and the system retries generation. If code synthesis loop is able to yield an expression which
computes $s$ within a maximum number of retries, the synthesis step succeeds with $e$. If the last generated
$e$ was invalid (resulting in an error), the code synthesis step fails with no expression. Otherwise, code
synthesis produces an expression $e$ but with a mismatched string outcome $s' \neq s$.

@@

The \InterpretationAgent is guided by a structured system prompt that frames code generation as a precise
replacement task. The model receives the imported datasets, helper modules, and the current Fluid
representation of the paragraph, in which a text fragment is marked with the tag \kw{[REPLACE …]}. The task is
to substitute this placeholder with a Fluid expression that evaluates exactly to the target string,
reconstructing quantitative or comparative claims as data queries. To ensure integration with the workflow,
the output must consist solely of a syntactically valid Fluid expression, with no additional commentary. The
full prompt is given in~\appref{system-prompt:interpretation-agent}.
